Using SMT engine to generate Symbolic Automata\thanks{This work was partially funded by the Associated Team FM4CPS between INRIA and ECNU, Shanghai}

### 2017-03-29 2017-Xudong-SMT/OpenPNets-SMT.tex
Introduction.
Merge introduction into the newest version.

>>>>

\QIN{
This paper presents our open automaton computing algorithm and its implementation in pNet API. Comparing the result of the algorithm with the manual result on the running example shows that the algorithm works properly in computing the open automaton for the pNet. The algorithm contains the method computing the open transitions composing the transitions from the subnets according to several defined rules the open transitions need to satisfy. These results are not the final results in fact, they still contain some unsatisfiable results we need to eliminate. To eliminate those unsatisfiability, we interact with an automatic theorem provers to use them for satisfiability checking. The translation of the pNet, mainly its presentation and its open transition predicates, is required for the implementation of the interaction.
}
